cleaning.qmd

### 2024-11-30 missing.qmd
Removing certain states

```{r}
combined <- read.csv('F24_STATS_FINAL/combined.csv')
```

@@

```{r}
sub.mods <- with(sub.imp, #replace with. model
)
summary(pool(sub.mods))

>>>>

```{r}
combined <- read.csv('https://github.com/wujenny214/F24_STATS_FINAL/raw/refs/heads/main/combined.csv')
```

@@

```{r}
sub.mods <- with(sub.imp, #replace with. model
)
summary(pool(sub.mods))
```

```{r}
head(combined.subset)
```

```{r}
combined.subset %>%
           group_by(State) %>%
           summarise(total_count = n(), Income_NA_count = sum(is.na(Median.Household.Income)), Uninsured_NA_count = sum(is.na(Percent.Uninsured.Adults)), Tax_NA_count = sum(is.na(Median.Prop.Tax)), Segregation_NA_count = sum(is.na(Residential.Segregation.Index)), Foods_NA_count = sum(is.na(Percent.Limited.Access.Healthy.Foods)), Expectancy_NA_count = sum(is.na(Life.Expectancy)), Adequacy_NA_count = sum(is.na(School.Funding.Adequacy)))
```

```{r}
summary(combined.subset)
```
